% --------------------------------------
%       PLEASE SEE README.MD
% --------------------------------------

\documentclass[
    letterpaper,
    10pt,
    unnumberedsections,
    twoside
]{LTJournalArticle}

\runninghead{Biomimetic Hydrogel for Tendon Repair}
\footertext{}

\usepackage{lipsum} % Lorem ipsum text for formatting
\usepackage{chemfig}
\usepackage{dblfloatfix}

\addbibresource{references_lucas.bib}
\addbibresource{references_edison.bib}
\addbibresource{references_luke.bib}
\addbibresource{references_matt.bib}

\title{Biomimetic Hydrogel for Tendon Repair}
\author{Lucas Chan, Luke Gailloux, Matt Levasseur, Edison Luke}

\renewcommand{\maketitlehookd}{%
    \begin{abstract}
        \noindent 
        Tendon injuries account for 30\% of all musculoskeletal clinical cases, accounting for around 4 million new cases worldwide per year. However, treatment is often a lengthy process, with severe cases taking a minimum of 12 weeks to resolve. Novel treatments have included hydrogels as a means to speed up tendon recovery, due to their ability to release therapeutics and healing factors in a local and targeted manner. Traditional hydrogels are limited in success though, due to their weak mechanical and adhesive properties. In contrast to traditional hydrogels, our proposed bio-inspired hydrogel is designed to have sufficient mechanical and adhesive properties through the use of a Janus Tough Adhesive (JTA) hydrogel in conjunction with a tough dissipative polymer matrix, along with self-healing capabilities. The various mechanisms and methods behind these superior properties will be explored. In addition to heightened mechanical and material properties, the novel JTA hydrogel uses targeted drug delivery and sustainable drug delivery to ensure optimal recovery. Finally, the proposed JTA hydrogel will be degradable and biocompatible, ensuring maximum compatibility with the human body. Through in-vivo testing of similar developing JTA hydrogels, the novel proposed hydrogel shows promise in revolutionizing tendon repair through exhibiting superior mechanical and material properties, longevity, drug delivery, and degradability.
        
    \end{abstract}
}

\setlength{\parskip}{0pt plus 1pt}

\begin{document}
    \maketitle 

    \section{Introduction}

    \input{Subfiles/introduction.tex}

    \section{Problem Statement and Hypothesis}

    \input{Subfiles/problem_statement.tex}
    
    \section{Objectives and Specific Aims}

    \input{Subfiles/objectives_aims.tex}

    \section{Hydrogel Structure and Composition}

    \input{Subfiles/classification_structure.tex}

    \section{Self-Healing ``Smart'' Hydrogels}

    \input{Subfiles/self_healing.tex}

    \input{Subfiles/janus_interface.tex}

    \section{Mechanical Properties of Janus Tough Adhesive Hydrogels}

    \input{Subfiles/strength.tex}

    \section{Adhesive Properties of Janus Tough Adhesive Hydrogels}

    \input{Subfiles/adhesion.tex}

    \section{Targeted Drug Delivery}

    \input{Subfiles/drug_release.tex}

    \section{Biocompatibility}

    \input{Subfiles/biocompatibility.tex}

    \section{Degradation of the Hydrogel Scaffold}

    \input{Subfiles/degradation.tex}

    % Towards a Self-Healing JTA
    % Section header command contained in the subfile
    % for better figure formatting

    \input{Subfiles/self_healing_JTA.tex}

    \section{Expected Outcomes}

    \input{Subfiles/expected_outcomes.tex}

    \onecolumn
    \printbibliography
\end{document}